Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking

### 2021-04-22 博士/论文提交/adversarial_attack/TCSVT/latex/bare_jrnl.tex
润色
加作者信息

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_BC.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_DEF.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_FM.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IPR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IV.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_LR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_MB.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OCC.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OPR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OV.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_SV.png}
  \end{center}
      \caption{Attribute-based success-rate plots in OTB-2015.}
  \label{fig:globally_uav20l_1}
\end{figure*}

@@

\textit{Ablation Study: Influence of the Adversarial Patch Size} 
It's important to make the size of the adversarial patch small to avoid suspicion. In our experiment, we produce three different sizes of the adversarial patch, namely, 32-by-32, 16-by-16 and 8-by-8 to test the efficiency of their attacks.
As shown in Table, the 16-by-16 patch can achieve ? and its area only accounts for ?\% of the searched image area.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{images/patch_size/patch_size.png}
  \end{center}
  \caption{Influence of patch size.}
  \label{fig:patch_size_table}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.15\textwidth]{images/patch_size/32.jpg}
    \includegraphics[width=0.15\textwidth]{images/patch_size/16.jpg}
    \includegraphics[width=0.15\textwidth]{images/patch_size/8.jpg}
  \end{center}
  \caption{Influence of patch size.}
  \label{fig:patch_size_vis}
\end{figure}

@@

\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to two more state-of-the-art anchor-based trackers: AlexNet-based SiamRPN \cite{SiamRPN} and ResNet-based SiamRPN++ \cite{SiamRPN++} to verify the transferability to different tracking architectures.
SiamRPN uses an RPN network to perform location regression and target classification on the response maps. SiamRPN++ performs layer-wise and depth-wise aggregation to improve accuracy based on the effective training using the ResNet backbone. The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.379 while the performance of SiamRPN++ is decreased from 0.676 to 0.518. The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.

We further analyze the perfor-mance of our method with respect to 11 attributes in OTB-2015 [22]. As suggested in OTB [22], the attributes consistof out-of-view (OV), occlusion (OCC), illumination varia-tion (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM),background clutters (BC), motion blur (MB), and in-planerotation (IPR).

@@

\begin{table}[]
  \centering
  %\footnotesize
  %\tabcolsep=2.0pt
  \caption{Precision score with respect to the \textit{real / fake trajectory} on OTB2015.}
  \begin{tabular}{@{}cccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Method} & \multirow{2}{*}[-2pt]{Tracker} & \multirow{2}{*}[-2pt]{\begin{tabular}[c]{@{}c@{}}Attack\\ Cost(ms)\end{tabular}} & \multirow{2}{*}[-2pt]{\begin{tabular}[c]{@{}c@{}}Clean\\ Videos\end{tabular}} & \multicolumn{2}{c}{Perturbed Videos} \\ \cmidrule(l){5-6} 
   &  &  &  & Real Traj. & Fake Traj. \\ \midrule
  CSA & SiamRPN & 4720 & 0.851 & 0.458 & - \\
  FAN & SiamFC & 10 & 0.720 & 0.180&0.420 \\
  TTP & SiamRPN++ & 8 & 0.910 & 0.080&0.692 \\
  \midrule
  Ours & SiamFC++ & 0 & 0.861 & 0.048&0.928 \\ \bottomrule
  \end{tabular}
  \label{tab:untargeted}
\end{table}

@@

>>>>

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_BC.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_DEF.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_FM.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IPR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IV.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_LR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_MB.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OCC.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OPR.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OV.png}
    \includegraphics[width=0.32\textwidth]{images/OTB2015/success_plot_OPE_OTB100_SV.png}
  \end{center}
      \caption{Attribute-based success-rate plots in OTB-2015.}
  \label{fig:attr}
\end{figure*}

@@

\textit{Ablation Study: Influence of the Adversarial Patch Size} 
It's important to make the size of the adversarial patch small to avoid suspicion. In our experiment, we produce three different sizes of the adversarial patch, namely, 32-by-32, 16-by-16 and 8-by-8 (Figure \ref{fig:patch_size_vis}) to test the efficiency of their attacks. During training and test, the patch size is fixed. We evaluate the AO score of SiamFC++ on the perturbed GOT-10 Val dataset.
As shown in Figure \ref{fig:patch_size_table}, the 16-by-16 patch can make the AO score drop dramatically to 0.12 and its area only accounts for 0.39\% of the searched image area.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{images/patch_size/patch_size.png}
  \end{center}
  \caption{Influence of the adversarial patch size. The 16-by-16 patch can make the AO score drop dramatically to 0.12 and its area only accounts for 0.39\% of the searched image area.}
  \label{fig:patch_size_table}
\end{figure}

\begin{figure}
  \centering
  \subfigure[32$\times$32]{\label{fig:a}\includegraphics[width=0.15\textwidth]{images/patch_size/32.jpg}}
  \subfigure[16$\times$16]{\label{fig:b}\includegraphics[width=0.15\textwidth]{images/patch_size/16.jpg}}
  \subfigure[8$\times$8]{\label{fig:c}\includegraphics[width=0.15\textwidth]{images/patch_size/8.jpg}}
  \caption{Adversarial patches of different sizes.}
  \label{fig:patch_size_vis}
\end{figure}

@@

\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to two more state-of-the-art anchor-based trackers: AlexNet-based SiamRPN \cite{SiamRPN} and ResNet-based SiamRPN++ \cite{SiamRPN++} to verify the transferability to different tracking architectures.
SiamRPN uses an RPN network to perform location regression and target classification on the response maps. SiamRPN++ performs layer-wise and depth-wise aggregation to improve accuracy based on the effective training using the ResNet backbone. The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.379 while the performance of SiamRPN++ is decreased from 0.676 to 0.518. We further analyze the perfor-mance of our method with respect to 11 attributes in OTB-2015 [22]. As suggested in OTB [22], the attributes consistof out-of-view (OV), occlusion (OCC), illumination varia-tion (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM),background clutters (BC), motion blur (MB), and in-planerotation (IPR). Figure \ref{fig:attr} illustrates the results of the aforementioned trackers under the 11 attributes. The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.

@@

\begin{table}[t]
  \centering
  \caption{Precision score with respect to the real/fake trajectory on OTB2015.}
  \begin{tabular}{@{}cccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Method} & \multirow{2}{*}[-2pt]{Tracker} & \multirow{2}{*}[-2pt]{\begin{tabular}[c]{@{}c@{}}Attack\\ Cost(ms)\end{tabular}} & \multirow{2}{*}[-2pt]{\begin{tabular}[c]{@{}c@{}}Clean\\ Videos\end{tabular}} & \multicolumn{2}{c}{Perturbed Videos} \\ \cmidrule(l){5-6} 
   &  &  &  & Real Traj. & Fake Traj. \\ \midrule
  CSA & SiamRPN & 4720 & 0.851 & 0.458 & - \\
  FAN & SiamFC & 10 & 0.720 & 0.180&0.420 \\
  TTP & SiamRPN++ & 8 & 0.910 & 0.080&0.692 \\
  \midrule
  Ours & SiamFC++ & 0 & 0.861 & 0.048&0.928 \\ \bottomrule
  \end{tabular}
  \label{tab:untargeted}
\end{table}

@@

% 作者
%\vfill  % 距离更远了
\enlargethispage{-5in}  % 距离近了些
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/zhbli.jpg}}]{Zhenbang Li}
received the B.S. degree in computer science and technology from Beijing Institute of Technology, Beijing, China, in 2016. Currently, he is a Ph.D. student in Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include object tracking and deep learning.
\end{IEEEbiography}
